resistanceModelNotesAndy

### 2016-05-16 paper2_resistance_mechanisms_mixtures.Rmd
progress

*to help explain I could start from a scenario where the attributes of each insecticide are the same*
*and then explore changing each in turn*
*I could then work up to the curtis fig2 plot*

@@

Parameter  | relative performance mix versus seq | Mechanism
------------------ | ------- | ---------------------------------------------------
A. All equal | seq > mix | resistance to the two insecticides in a mixture increases at a similar rate and is reached sooner than if the insecticides are applied individually in sequence
1. Effectiveness | faster | ...
2. Exposure | faster | ...
3. Dominance | faster | ...
4. Selection Coefficient | ...
5. Frequency  | faster | ...

>>>>

*to help explain I could start from a scenario where the attributes of each insecticide are the same*
*and then explore changing each in turn*
*I could then work up to the curtis fig2 plot*
*could in each case incease value of I1 by 0.2 or some other value*

@@

Parameter  | relative performance mix versus seq | Mechanism
------------------ | ------- | ---------------------------------------------------
A. All equal | seq > mix | resistance to the two insecticides in a mixture increases at a similar rate and is reached sooner than if the insecticides are applied individually in sequence
1. Effectiveness | mix > seq | resistance to the more effective insecticide increases ...
2. Exposure | faster | ...
3. Dominance | faster | ...
4. Selection Coefficient | ...
5. Frequency  | faster | ...

### 2016-05-16 resistanceModelNotesAndy.Rmd
updating paper2
progress

@@

@@

>>>>

Update Report for Ian :

Tsetse : 15 days remaining : defined things to do for Steve
Resistance : 55 days (from 85) remaining

@@

~ set up a new UI allowing comparison of 2 model runs side by side (like my curtis one but be able to modify params for both plots)
~~ quickest would just be to add extra inputs on bottom

@@

# time
To the end of Feb :
Hours		105:45:00
Hours rounded		105.00
Days (/7.5)		14.00
Days remaining (from 85)		71.00

march, april :
Hours 124.5
Days (/7.5)		16.6
Days previous 71
Days remaining (from 85)		71-16.6 = 54.4
